---
title: "p8105_hw1_zv2138"
output: github_document
---

```{r Setup}
library(tidyverse)
```

Problem 1 

```{r Creating the df}
problem_1_df = tibble(
  random_samp = rnorm(10),
  is_positive = random_samp > 0,
  cat_names = c('Susan', 'Helen', 'Sally', 'Matt', 'George', 'Paolo', 'Oliver',
               'Zoe', 'Paul', 'Laura'),
  cats_colors = factor(c("Black", "White", "Red", "Black", "Red", "Red",
                         "Black", "White", "White", "Black"))
)
```


```{r Mean}
mean(pull(problem_1_df, random_samp))
mean(pull(problem_1_df, is_positive))
mean(pull(problem_1_df, cat_names))
mean(pull(problem_1_df, cats_colors))
```

What works and what doesn’t?

I was able to take the mean of my random_samp variable. This makes sense to me because we are taking the mean value from a set of 10 numbers.

I was able to take the mean of my is_positive variable. This produced a numeric output. This doesn't make sense to me because this variable is of type logic and stores True and False values. It doesn't make sense that R thinks you can take the mean of True and False statements. 

I was not able to take the mean of my character vector cat_names. My function returned NA. This makes sense to me because this vector holds characters. You can not take the mean of a set of characters.

I was not able to take the mean of my factor vector. My function returned NA. This makes sense to me because the input argument is not numeric. 


```{r Mean with as.numeric, results='hide', warning=F}
as.numeric(pull(problem_1_df, is_positive))
as.numeric(pull(problem_1_df, cat_names))
as.numeric(pull(problem_1_df, cats_colors))
```

What happens, and why? Does this help explain what happens when you try to take the mean?

My logical vector was converted into a list of numeric 1's and 0's. It seems that R stores logical variables as either a 0 for FALSE or a 1 for TRUE. This makes sense why we were able to take the mean of my logical is_positive variable because R is calculating the mean of 10 numbers made up of 0's and 1's. 

My character vector called cat_names returned a list of 10 NAs. This makes sense why we were not able to return a mean value. Character strings can not be formated into numbers so a mean can not be cacluated so my mean function feturn NA.  

My factor vector returned a list of 1's, 2's, and 3's. These numbers correspond to what level each vector entry is coded for. For example Black is coded as level 1, Red as level 2 and White as level 3. 


